---
title: "linzhao_new_dv_vege"
author: "Lin Zhao"
date: "4/25/2020"
output: 
 html_notebook:
    default
 html_document:
    default
---

#import resturant csv to my computer
```{r}
data1 <- read.csv("/Users/lin/Desktop/Restaurant.csv")
head(data1)
```


```{r}
class(data1$cuisines)
```

```{r}
a <- as.character(data1$cuisines) 
```

#I am trying to identity which resturant is vegetarian 
```{r}
library("stringr")
vege <- str_detect(a,"Vegetarian")
data2 <- cbind(vege,data1)
```


#Filter out the restaurant which is not vegetarian

```{r}
class(data2$vege)
data2$vege <- as.numeric(data2$vege)
```


#do the subset for vege
```{r}
library(dplyr)
data3 <- subset(data2,vege==1) 
```



## create a new dataset that I convert to lat and lon to the county level
```{r}
library(dplyr)
data4 <- data3 %>% 
  select(id,city,name,latitude, longitude,phones,paymentTypes,postalCode) %>% 
  na.omit()
View(data4)
```



```{r}
library(sp)
library(maps)
library(maptools)

# The single argument to this function, pointsDF, is a data.frame in which:
#   - column 1 contains the longitude in degrees (negative in the US)
#   - column 2 contains the latitude in degrees

latlong2county <- function(pointsDF) {
    # Prepare SpatialPolygons object with one SpatialPolygon
    # per county
    counties <- map('county', fill=TRUE, col="transparent", plot=FALSE)
    IDs <- sapply(strsplit(counties$names, ":"), function(x) x[1])
    counties_sp <- map2SpatialPolygons(counties, IDs=IDs,
                     proj4string=CRS("+proj=longlat +datum=WGS84"))

    # Convert pointsDF to a SpatialPoints object 
    pointsSP <- SpatialPoints(pointsDF, 
                    proj4string=CRS("+proj=longlat +datum=WGS84"))

    # Use 'over' to get _indices_ of the Polygons object containing each point 
    indices <- over(pointsSP, counties_sp)

    # Return the county names of the Polygons object containing each point
    countyNames <- sapply(counties_sp@polygons, function(x) x@ID)
    countyNames[indices]
}

# Test the function using points in Wisconsin and Oregon.
testPoints <- data.frame(x = data4$longitude, y = data4$latitude)

county_list<- latlong2county(testPoints)
```


```{r}
county_list_data <- as.data.frame(county_list)
data5 <- cbind(data4,county_list_data) #merge to data4 by adding a column named county_list
```



```{r}
data5 <- data5 %>% 
  na.omit()
unique(data5$county_list)
```


#regular expression for ny vege restaurant data
```{r}
county_name <- as.character(data5$county_list)
# Remove all before and up to ",":
county_name2 <- gsub(".*,","",county_name)
data6 <- cbind(county_name2,data5)  
data6$county_list <- NULL
data6
```


```{r}
unique(data6$county_name2)
```


#import election data 
```{r}
eleccounty<-read.csv("/Users/lin/Desktop/2016_US_County_Level_Presidential_Results.csv")

eleccounty$X1 <- NULL

eleccounty <- eleccounty %>% 
         filter(state_abbr=="NY") #there are 62 counties in NY State

```

#do some regular expression on election data

```{r}
foo <- as.character(eleccounty$county_name)
```


```{r}
foo2 <- gsub("\\s*\\w*$", "", foo)
foo3 <- tolower(foo2)
foo4 <- str_replace(foo3, "st. lawrence", "st lawrence")
foo4
```

#regular expression of final step for election data
```{r}
new_eleccounty <- cbind(eleccounty,foo4)

names(new_eleccounty)[names(new_eleccounty) == 'foo4'] <- 'county_name2'
```


#calculate who is win in 2016 on the county level
```{r}
new_eleccounty <- new_eleccounty %>% 
  mutate(difference_in_vote=votes_gop-votes_dem) %>% 
  mutate (R.D= ifelse(difference_in_vote > 0, "Republican", "Democrat"))
``` 


#combine cleaned ny vege reastaurant with election county data in 2016

```{r}
#left outer join
df <- left_join(data6, new_eleccounty,by = "county_name2")

df$paymentTypes <- as.character(df$paymentTypes)
df$paymentTypes[df$paymentTypes==""] <- "NA"
df$paymentTypes <- as.factor(df$paymentTypes)
```



#make a leaflet map of vege restaurant in NY States


```{r}

library(leaflet)

library(RColorBrewer)

pal = colorFactor(palette = c("blue", "red"), domain = df$R.D) # Grab a palette
color_vote = pal(df$R.D)

content2 <- paste("County:",data6$county_name2,"<br/>",
                 "Restaurant Name:",data6$name,"<br/>",
                 "Phones:",data6$phones,"<br/>",
                 "PaymentType:",data6$paymentTypes,"<br/>",
                 "PostCode:",data6$postalCode,"<br/>"
                 )


content3 <- paste("County:",df$county_name,"<br/>",
                 "Restaurant Name:",df$name,"<br/>",
                 "Phones:",df$phones,"<br/>",
                 "PaymentType:",df$paymentTypes,"<br/>",
                 "PostCode",df$postalCode,"<br/>"
                 )
                
m2 <- leaflet(data=data6) %>%
   # Base groups
  addTiles(group = "OSM (default)") %>%
  addProviderTiles(providers$Stamen.Toner, group = "Toner") %>%
  addProviderTiles(providers$Stamen.TonerLite, group = "Toner Lite") %>%
   # Overlay groups
  addCircles(
             color="green",
             lng = ~longitude, 
             lat = ~latitude,
             popup = content2,
             group = "Vegetarian Restaurants") %>% 
  addCircleMarkers(data = df, 
             lng = ~longitude, 
             lat = ~latitude,
             popup = content3,
             group = "Political Ideology",
             color= color_vote) %>%
  addLegend(pal = pal, values = ~df$R.D, title = "Won Party in 2016") %>% 
  # Layers control
  addLayersControl(
    baseGroups = c("OSM (default)", "Toner", "Toner Lite"),
    overlayGroups = c("Vegetarian Restaurants", "Political Ideology"),
    options = layersControlOptions(collapsed = FALSE)
  )

m2

```

